---
title: "Lattice"
author: "Janeci Leoni Dewes"
date: "10/24/2020"
output: html_document
---


## Lattice package

The Lattice package is a high-level data visualization system with an emphasis on multivariate data.

When creating graphs, conditions and groupings are 2 concepts
that allow us to more easily understand the data at hand.
The concept behind Lattice is to group data and create visualizations in a way that makes it easier to search for patterns.

```{r}
# Instalar e carregar o pacote
# install.packages('lattice')
library(lattice)
```

## ScatterPlot

You can also embed plots, for example:

```{r}
# ScatterPlot com Lattice (dataset iris)
# fç xyplot
xyplot(data = iris, groups = Species, Sepal.Length ~ Petal.Length)
```

## BarPlot

```{r}
# BarPlots com dataset Titanic (dataset da ling R)

# fç usada é o barchart
barchart(Class ~ Freq | Sex + Age, data = as.data.frame(Titanic),
         groups = Survived, stack = T, layout = c(4, 1),
         auto.key = list(title = "Dados Titanic", columns = 2))

barchart(Class ~ Freq | Sex + Age, data = as.data.frame(Titanic),
         groups = Survived, stack = T, layout = c(4, 1),
         auto.key = list(title = "Dados Titanic", columns = 2),
         scales = list(x = "free"))
```


```{r}
# Contagem de elementos
# Dataset iris 
PetalLength <- equal.count(iris$Petal.Length, 4)
PetalLength
```


```{r}
# ScatterPlots 
xyplot(Sepal.Length~Sepal.Width | PetalLength, data = iris)
# relação de duas variaveis com outra (uma) variável
```

```{r}
xyplot(Sepal.Length~Sepal.Width | PetalLength, data = iris,
       panel = function(...) {
         panel.grid(h = -1, v = -1, col.line = "skyblue")
         panel.xyplot(...)})

```
```{r}
# add lm
xyplot(Sepal.Length~Sepal.Width | PetalLength, data = iris,
       panel = function(x,y,...) {
         panel.xyplot(x,y,...)
         mylm <- lm(y~x)
         panel.abline(mylm)})
# lm modelo de regressão(preditivo)
```

```{r}
# Histograma das 3 distrib.
histogram(~Sepal.Length | Species, xlab = "",
          data = iris, layout=c(3,1), type = "density",
          main = "Histograma Lattice", sub = "Iris Dataset, Sepal Length")
```
```{r}
# Distribuição dos dados
qqmath(~ Sepal.Length | Species, data = iris, distribution = qunif)
```
```{r}
# Boxplot
bwplot(Species~Sepal.Length, data = iris)
```

```{r}
# ViolinPlot
bwplot(Species~Sepal.Length, data = iris,
       panel = panel.violin)
```

OBS: o pacote lattice é muito útil para análise de dados, principalmente para
comparação de diversas variáveis.

Fim
